### 2023-10-02 1.Introduction/motivation.tex
Much else to add, need inspi

The point of this thesis is to lay out the ground work to create a LSTM capable chip to use in embedded systems. It could be used detection and prediction of any kind of sequential events.

>>>>

The focus of this thesis is to create a working simulation of an analog \ac{LSTM} circuit using Cadence's virtuoso as simulation software. Having those preliminary results would allow for fabricating and testing such a chip. Once a working prototype is manufactured, such a circuit could highly improve embedded \ac{AI} use.
